\sysfull

### 2018-08-07 paper/asplos19/systemdescription.tex
System description revised

\paragraph{Virtual Memory Manager.}
\sys can coalesce tasks thanks to its virtual memory manager (VMM). VMM privatizes memory pages demanded by a coalesced task and limits application accesses only to the fast volatile memory. VMM keeps all page modifications in non-volatile memory on a coalesced task transition. VMM also solves a novel data consistency problem we call \emph{coalescing-induced WAR dependency}. Section~\ref{sec:memory_virtulaization} outlines VMM.

>>>>

\paragraph{Virtual Memory Manager.}
\sys virtual memory manager (VMM) is the key enabler to ensure memory consistency while coalescing tasks. VMM allows applications to interface with only fast volatile memory pages and privatizes the modified pages demanded by a coalesced task in order to solve a novel data consistency problem; namely \emph{task coalescing-induced WAR dependency}. VMM achieves page privatization by keeping all page modifications in non-volatile memory on a coalesced task transition. Section~\ref{sec:memory_virtulaization} outlines VMM.
